### 2017-01-19 paper/evaluation.tex
pass on intro
Added note about subjects that require additional arguments to run all tests

Given that \percentMedLongRunning{} of the projects are costly (\ie,
\numMedLong{} projects from \medg{} and \longg{}), we concluded that
time-consuming regression test suites are relatively frequent in
open-source projects.  It is important to mention that
Figure~\ref{fig:rq1-barplot} represents a lower bound for time cost:
some tests may finish early due to a failure since a subject may be
tested in a failing revision. From the \numSubjs{} projects, 286
passed all tests and 118 had failures. \Jbc{elaborate failed subjects:
how much \% of the tests failed?}

@@

Overall, results indicate that projects with a very small number of
tests monopolizing the CPU were not predominant.

>>>>

Given that \percentMedLongRunning{} of the projects are costly (\ie,
\numMedLong{} projects from \medg{} and \longg{}), we concluded that
time-consuming regression test suites are relatively frequent in
open-source projects.  It is important to mention that
Figure~\ref{fig:rq1-barplot} represents a lower bound estimation for
time cost because some projects omit long-running tests on their
default execution. For instance, it is necessary to invoke Maven with
additional parameters to run integration tests from project
\CodeIn{apache.maven-surefire} (nearly 30 min in our environment).
Also, some tests may finish earlier than expected due to existing bugs
on the ongoing revision.  From the \numSubjs{} compiled projects, 286
successfully executed all tests and 118 reported test failures.
\Jbc{elaborate failed subjects: how much \% of the tests failed?}

@@

Overall, results indicate that projects with a very small number of
tests monopolizing end-to-end execution time were rare.
